Compositional equivalences based on Open pNets

### 2020-02-04 2016-Weak-FH-Bisim/WeakBisim.tex
new proposal page 22

$$ 1 = \openrule
         {\{P\mapsto\texttt{p-a}\}, [\forall m.p-a!=P\_send(m)], () }
         {000 \OTWeakarrow {\texttt{p-a}} 000}$$
\\
$$6 = \openrule
         {\{\}, [True], () }
         {100 \OTWeakarrow {\tau\big(\subst{m1\_c:=s1\_c,m1\_m:=s1\_m,s2\_c:=s1\_c}\subst{s1\_c:=s2\_c+1}\big)^* \subst{m1\_c:=s1\_c,m1\_m:=s1\_m,s2\_c:=s1\_c} } 210}
         $$

>>>>

Here I denote as $post_n$ the effect of the Strong transition $OT_n$ from Figure \ref{}:
$$post_3 = (s1\_c\gets 0, s1\_m\gets m)$$
$$post_4 = (m1\_msg\gets s1\_msg, m1\_c\gets s1\_c)$$
$$post_5 = (m2\_c\gets m1\_c)$$
$$post_6 = (s1\_c\gets m2\_c+1)$$

Then the effect of one single $100 -> 210 -> 220 -> 100$ loop as:
$$Post_{456} = post_6\shortotimes post_5\shortotimes post_4$$

And $WOT_4$ becomes:
$$ 3 = \openrule
         {\{P\mapsto\texttt{p\_send(m)}\}, True, post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3}
         {000 \OTWeakarrow {\texttt{in(m)}} 100}$$
\\
$$4 = \openrule
         {\{\}, True, post_4\shortotimes {Post_{456}}^* }
         {100 \OTWeakarrow {\tau} 210}
         $$
